Response to the defense feedback

### 2021-05-31 Chapter-5/Chapter-5.tex
Updates from Overleaf

We evaluate \ctool{} on TinyDNN, a deep learning framework in C++. We construct a LeNet-5 model~\cite{lecun1998gradient} and train it with the MINIST dataset. LeNet-5 network has six layers, including three convolutional layers, one fully connected layer and two pooling layers. The batch size in our experiment is 10, and the number of epochs is 30. After the training, the accuracy of the neural networks on test set images is 99.5\%. Then we use the model to infer the images. The inference dataset consists of $10000$ images.  During the inference, we record the memory access information. The evaluation shows that all three types of layers have different memory accesses under different inputs. In addition, we find that the leakages primarily come from the activation function and the image convert function.

>>>>

We evaluate \ctool{} on TinyDNN, a deep learning framework in C++. We
construct a LeNet-5 model~\cite{lecun1998gradient} and trained it with
the MINIST dataset. LeNet-5 network has six layers, including three
convolutional layers, one fully connected layer, and two pooling
layers. The batch size in our experiment is 10, and the number of
epochs is 30. After the training, the accuracy of the neural networks
on test set images is 99.5\%. Then we use the model to infer the
images. The inference dataset consists of $10,000$ images.  During the
inference, we record the memory access information. The evaluation
shows all three types of layers have different memory accesses under
different inputs. We find that the leakages primarily come from the
activation function and the image convert function.
